This is an example of article title

### 2024-05-31 paper/paper.tex
remove comments

%TODO: ez túl sok helyet foglal
\iffalse
The paper is structured as follows: the multi operation blank localization algorithm is introduced briefly in Sec.~\ref{sec:algo}, followed by the requirements and needs showed up during development in Sec.~\ref{sec:req} and the solutions of those problems in Sec.~\ref{sec:approach}.
Finally a short example is given in Sec.~\ref{sec:results} and the paper is concluded in Sec.~\ref{sec:conclusion}.
\fi

@@

Measurements of the rough parts can be obtained with a variety of instruments, including coordinate measurement machines (CMM), laser scanners, measurement arms, etc.
The two main representations that these devices create are primitive geometries (cylinders, planes, etc.) and free-form geometries in the form of point cloud or triangulated mesh.
These measurements are fed into the optimization model, which is a convex quadratically constrained quadratic program (QCQP).
Details of the optimization model can be found in the papers \cite{cserteg:2023_Annals} and \cite{cserteg:2023_CMS}.
%TODO: ide kéne még egy bekezdés arról, hogy mi is a modell?
% a mérések alapján -> QCQP ????
% a free-form / primitive-ről sem írtam még

\iffalse
The method gives engineers a tool to balance between machining allowance and tolerance error.
Former is
Machining allowance is calculated for each feature as the smallest thickness of the material to be removed.
Tolerance error is defined for each dimensional tolerance record, that is defined between to features.
Their distance has a nominal value and upper-lower bounds.
The goal of the algorithm is to keep the tolerance distances close to the nominal value, while keeping a minimum machining allowance value.
\fi

\section{Implementation in Julia}
%\section{Approach}
\label{sec:approach}

During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner as well.
These needs include:
% (high-level, programozói igények nélkül, amit egy menedzser felsorolna):

\begin{itemize}
	\item A versatile type system for geometrical representation, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
	\item Easy-to-use interface for the optimization model.
	\item Support for importing geometries from a variety of measurement tools (CMM, laser scanner, measurement arm).
	\item Support for debugging, analyzing and visualizing the results.
%	\item Handling the differences of drilling and milling (hole and plane geometries).	
%	\item Model the problem, including geometry representaton, qcqp model building and solving, evaluation, visualization.
%	\item Modeling the different behavious of the geometries (holes, planes)
%	\item Handle two basic types of measurements: primitive or free-form.
%	\item Support for importing geometries: all kinds of measurement (expandable/extendable? type system for introducing new measurement types)
\end{itemize}

@@

As mentioned earlier, an important requirement was to handle the output formats of many different devices.
Every measurement instrument comes with its own processing software and export formats, not necessarily designed for interoperability.
As a result, we needed to write (or use) parsers for different text and tabular formats.
%The measurement results are read into their own respective type that implements the internal API, which means that

@@

\iffalse
Tasks are defined in the workpiece coordinate frame (called workpiece datum).
Two types of geometries need to be aligned: rough and machined. Currently the algorithm, thus the implementation supports two types of features: holes and planes.
A flexible type system is implemented: abstract types are defined and all methods act on them, so implementing a new geometry type (for example to handle point cloud measurement of a rough hole) means defining the type and those methods.
All other functionality of the package are working automatically: setting up the optimization model, solving it, evaluating the results in details and visualizing the geometries.
\fi

\section{Results and future work} %TODO: or Example
\label{sec:results}

@@

%TODO: future works
% - tolerance modeling
% - discover other machining operations (turning)
% - add more examples to docs

>>>>

@@

Measurements of the rough parts can be obtained with a variety of instruments, including coordinate measurement machines (CMM), laser scanners, measurement arms, etc.
The two main representations that these devices create are primitive geometries (cylinders, planes, etc.) and free-form geometries in the form of point cloud or triangulated mesh.
These measurements are fed into the optimization model, which is a convex quadratically constrained quadratic program (QCQP).
Details of the optimization model can be found in the papers \cite{cserteg:2023_Annals} and \cite{cserteg:2023_CMS}.

\section{Implementation in Julia}
\label{sec:approach}

During the development of the algorithm, we needed an environment (package) that supports the quick prototyping needs of research, while giving a solid foundation to validate the concept with our industry partner as well.
These needs include:

\begin{itemize}
	\item A versatile type system for geometrical representation, especially regarding the differences of drilling/milling operations and free-form/primitive geometry representation.
	\item Easy-to-use interface for the optimization model.
	\item Support for importing geometries from a variety of measurement tools (CMM, laser scanner, measurement arm).
	\item Support for debugging, analyzing and visualizing the results.
\end{itemize}

@@

As mentioned earlier, an important requirement was to handle the output formats of many different devices.
Every measurement instrument comes with its own processing software and export formats, not necessarily designed for interoperability.
As a result, we needed to write (or use) parsers for different text and tabular formats.

@@

\section{Results and future work}
\label{sec:results}

@@
